\subsection{Group Tasks}
    Assigned following roles to:
	\begin{itemize}
		\item Team Leader: Keith Hand
		\item Facilitator: Logan Anderson
		\item Minute Taker: Jesse Quach
		\item Timekeeper: Logan Thurm
    \end{itemize}

\subsection{Project Introduction}
    Going over Programming Language: \newline
	
		\textbf{Ruby:}	
		\begin{itemize}
			\item Pros: Great for API usage.
			\item Cons: None of the group members are familiar with Ruby.
		\end{itemize}
		\newpage
		\textbf{PHP:}	
		\begin{itemize}
			\item Pros: Well documented and widely used in web development as well as being easy to use with databases.
			\item Cons: Lack of clarity from given error exceptions as well as lack of basic knowledge of the language within the group
		\end{itemize}
		
	\emph{\small{Will most likely use PHP}} \newline\newline
	Going over Version Control:
	\begin{itemize}
		\item Github: Excellent documentation (every change is noted) so changes can be made in real-time
		as well as ensuring corrupted code is removed as every change must be documented before 
		change is put through. Branches will also allow all members of the group to work 
		independently of one another and simply combine tasks delegated into one in the end.
	\end{itemize}
	Going over Server Control:
	\begin{itemize}
		\item Keith: will utilize [my] Raspberry-Pi to establish server.
	\end{itemize}

\subsection{Project Estimation}
    Setting up base project:
	\begin{itemize}
		\item Install PHPStorm
		\item Install Docker (Virtual Machine)
	\end{itemize}
	API Research:
	\begin{itemize}
		\item How to implement API within PHP.
	\end{itemize}
	Programming Language Research:
	\begin{itemize}
		\item Find examples (fundamental and basics) over PHP.
	\end{itemize}